---
title: "Data 605 Week 4 Assignment"
author: "Tyler Baker"
date: "2/19/2022"
output: html_document
---

```{r}
library(tidyverse)
library(jpeg)
library(OpenImageR)
library(magick)
library(imager)
```

# Step 1 

for the first step I needed to load the data. Figuring out how to load JPEG data was much harder than I thought. I was able to find a solution to loading the data from a forum on Stackoverflow.
```{r}
files<- list.files(path = "C:\\Users\\tyler\\Downloads\\DATA 605\\jpg", pattern = ".jpg", full.names = TRUE)
df<- image_info(image_read(files))
df$file_name <- files
```

# Step 2

I wanted to plot the images to see what exactly we were working with.
```{r}
length <- 1:17
load_images <- for (i in length){
  image<- load.image(df$file_name[i])
  plot(image)
}
```

# Step 3

This is where the assignment became very difficult. I wanted to turn each image into a matrix. Then I would combine the matrices into one giant matrix which I would then try to find the eigenvectors and eigenvalues for using the eigen() function. Unfortunately, I was unable to succeed in my goal. 

```{r}
shoes <- as.data.frame(image)
```
This caused an error because the matrix didn't look appropriate to the data. It only gave back 4 columns. Three of these columns were full of only ones. So I tried a different approach.

```{r}
shoe_image_one <- load.image((df$file_name[1]))
shoe_one <- matrix(shoe_image_one)
shoe_image_two <- load.image((df$file_name[2]))
shoe_two<- matrix(shoe_image_two)
shoe_image_three <- load.image((df$file_name[3]))
shoe_three<- matrix(shoe_image_three)
shoe_image_four <- load.image((df$file_name[4]))
shoe_four<- matrix(shoe_image_four)
shoe_image_five <- load.image((df$file_name[5]))
shoe_five<- matrix(shoe_image_five)
shoe_image_six<- load.image((df$file_name[6]))
shoe_six<- matrix(shoe_image_six)
shoe_image_seven <- load.image((df$file_name[7]))
shoe_seven<- matrix(shoe_image_seven)
shoe_image_eight <- load.image((df$file_name[8]))
shoe_eight<- matrix(shoe_image_eight)
shoe_image_nine <- load.image((df$file_name[9]))
shoe_nine<- matrix(shoe_image_nine)
shoe_image_ten <- load.image((df$file_name[10]))
shoe_ten<- matrix(shoe_image_ten)
shoe_image_eleven <- load.image((df$file_name[11]))
shoe_eleven<- matrix(shoe_image_eleven)
shoe_image_twelve <- load.image((df$file_name[12]))
shoe_twelve<- matrix(shoe_image_twelve)
shoe_image_thirteen <- load.image((df$file_name[13]))
shoe_thirteen<- matrix(shoe_image_thirteen)
shoe_image_fourteen <- load.image((df$file_name[14]))
shoe_fourteen<- matrix(shoe_image_fourteen)
shoe_image_fifteen <- load.image((df$file_name[15]))
shoe_fifteen<- matrix(shoe_image_fifteen)
shoe_image_sixteen <- load.image((df$file_name[16]))
shoe_sixteen<- matrix(shoe_image_sixteen)
shoe_image_seventeen <- load.image((df$file_name[17]))
shoe_seventeen<- matrix(shoe_image_seventeen)

shoes<- cbind(shoe_one, shoe_two, shoe_three, shoe_four, shoe_five, shoe_six, shoe_seven, shoe_eight, shoe_nine, shoe_ten, shoe_eleven, shoe_twelve, shoe_thirteen, shoe_fourteen, shoe_fifteen, shoe_sixteen, shoe_seventeen)
```
This time I got 17 columns like I had wanted. However, It appears that most of the values were just a 1 again. 

```{r}
# eigen(shoes) will be an error because shoes is non-square.
#Therefore, I will instead times shoes by its transpose to give me a square matrix.

#square_shoes <- shoes %*% t(shoes)
```
This became such a big matrix that it wasn't able to compute.

# Next steps

If my data was loaded and managed properly I was expecting to get 17 columns were the values were slightly different from each other. Then I would have found the eigenvalues and the eigenvectors. I also would have found the mean and covariance. After that I am still unsure of what I would do. 

# Final Thoughts

This assignment was very hard. This is the first time that I have felt out right lost. I feel comfortable with linear algebra. I need to work on statistics and probability more. But understanding how to combine and apply them to problems is very new. I would love to see an example of what I was supposed to do.
